Meta-analytic approaches and effect sizes to account for 'nuisance heterogeneity' in comparative physiology

### 2021-09-18 MS/ms.Rmd
Added refs to the examples of effect size metrics

The key features of all effect sizes used in meta-analyses are that: 1) they are statistical parameters that have been placed on a common scale so that they can be compared across studies and 2) they have some associated measure of precision (i.e., sampling variance) [@Koricheva2013; @Borenstein2009; @Schmid2021]. Effect sizes in comparative physiology are quite diverse; they can be the mean difference between two groups [e.g., difference in mean between a control and treatment group; e.g., @WuSeebacher2020], the slope of a regression (e.g., between body size and metabolic rate), a correlation between two variables (e.g., between hormone levels and behaviour), or even the raw mean (or variance) itself [e.g., comparing CTmax or CTmin across species - e.g., @Sunday2014]. In many cases, different effect sizes might be used depending on the question. For example, to investigate the effect of temperature on a physiological trait, one can compile studies experimentally manipulating temperature and analyse the mean 'effect' by creating contrast-based effect sizes, or alternatively, just model the trait in each temperature treatment. The choice as to which one to use boils down to the types of data available from primary studies, the specific question of interest, and whether studies are observational or experimental in nature. Considering our temperature example above, if we are interested in the magnitude of change between temperature treatments, we may want to use a contrast-based effect size, such as the log response ratio, *$\ln{RR}$*. Instead, if we are interested in how the mean of some physiological trait changes with temperature, we may model the mean itself. In the latter scenario, as long as all the means are measured in the same units (e.g., degrees Celsius) or can be converted to the same units, then the mean may provide the desired answer to the original question. We provide details on different effect measures and associated sample sizes in Table \@ref(tab:tablea).

>>>>

The key features of all effect sizes used in meta-analyses are that: 1) they are statistical parameters that have been placed on a common scale so that they can be compared across studies and 2) they have some associated measure of precision (i.e., sampling variance) [@Koricheva2013; @Borenstein2009; @Schmid2021]. Effect sizes in comparative physiology are quite diverse; they can be the mean difference between two groups [e.g., difference in mean between a control and treatment group; e.g., @WuSeebacher2020], the slope of a regression [e.g., between body size and metabolic rate, @Uyeda2017], a correlation between two variables [(]e.g., between hormone levels and behaviour, @Holtman2016], or even the raw mean (or variance) itself [e.g., comparing CTmax or CTmin across species - e.g., @Sunday2014]. In many cases, different effect sizes might be used depending on the question. For example, to investigate the effect of temperature on a physiological trait, one can compile studies experimentally manipulating temperature and analyse the mean 'effect' by creating contrast-based effect sizes, or alternatively, just model the trait in each temperature treatment. The choice as to which one to use boils down to the types of data available from primary studies, the specific question of interest, and whether studies are observational or experimental in nature. Considering our temperature example above, if we are interested in the magnitude of change between temperature treatments, we may want to use a contrast-based effect size, such as the log response ratio, *$\ln{RR}$*. Instead, if we are interested in how the mean of some physiological trait changes with temperature, we may model the mean itself. In the latter scenario, as long as all the means are measured in the same units (e.g., degrees Celsius) or can be converted to the same units, then the mean may provide the desired answer to the original question. We provide details on different effect measures and associated sample sizes in Table \@ref(tab:tablea).
